Searching for standards of fairness in the transportation justice literature

### 2025-02-17 just-transportation/just-transportation.qmd
New definitions; revised manuscript. For Nacho review

---
title: "Searching for standards of fairness in the transportation justice literature"
subtitle: "Searching for standards of fairness"
format:
  mj-report-pdf: 
    keep-tex: true
doctype: "Report (Draft)"

# Author information. You can add or delete authors here
author:
  - name:
      given: Anastasia
      family: Soukhov
    affiliations: 
      - name: McMaster University
        department: School of Earth, Environment and Society
    email: soukhoa@mcmaster.ca
  - name:
      given: Ignacio
      family: Tiznado-Aitken
    affiliations: 
      - name: University of Toronto
        department: Department of Geography and Planning
    email: i.tiznadoaitken@utoronto.ca  
  - name:
      given: Matthew
      family: Palm
    affiliations: 
      - name: The University of North Carolina at Chapel Hill
        department: Department of City and Regional Planning
    email: palmmatt@unc.edu  
  - name:
      given: Steven
      family: Farber
    affiliations: 
      - name: University of Toronto
        department: Department of Geography and Planning
    email: steven.farber@utoronto.ca  
  - name:
      given: Antonio
      family: Páez
    affiliations: 
      - name: McMaster University
        department: School of Earth, Environment and Society
    email: paezha@mcmaster.ca

@@

# Place the cover image and the toc image in folder `images`
cover_image: cover-picture.png
cover_image_caption: "Source: Marco Verch (https://www.flickr.com/photos/160866001@N07/50597690137/)"
toc_image: toc-picture.png
toc_image_caption: "Source: Progressive Charlestown (https://www.progressive-charlestown.com/2020/01/amazon-drivers-die-for-you.html)"
# Information for generating citation
citation:
  type: report
  doi: "10.somenumber/document.00010"
  issued: last-modified
  url: https://example.com/summarizing-output
  number: "MJ-0001"
bibliography: bibliography.bib
---

>>>>

---
title: "Searching for standards of fairness in the transportation justice literature"
subtitle: "Searching for standards of fairness"
# format:
#   mj-report-pdf: 
#     keep-tex: true
# doctype: "Report (Draft)"

# Author information. You can add or delete authors here
# author:
#   - name:
#       given: Anastasia
#       family: Soukhov
#     affiliations: 
#       - name: McMaster University
#         department: School of Earth, Environment and Society
#     email: soukhoa@mcmaster.ca
#   - name:
#       given: Ignacio
#       family: Tiznado-Aitken
#     affiliations: 
#       - name: University of Toronto
#         department: Department of Geography and Planning
#     email: i.tiznadoaitken@utoronto.ca  
#   - name:
#       given: Matthew
#       family: Palm
#     affiliations: 
#       - name: The University of North Carolina at Chapel Hill
#         department: Department of City and Regional Planning
#     email: palmmatt@unc.edu  
#   - name:
#       given: Steven
#       family: Farber
#     affiliations: 
#       - name: University of Toronto
#         department: Department of Geography and Planning
#     email: steven.farber@utoronto.ca  
#   - name:
#       given: Antonio
#       family: Páez
#     affiliations: 
#       - name: McMaster University
#         department: School of Earth, Environment and Society
#     email: paezha@mcmaster.ca

@@

# Place the cover image and the toc image in folder `images`
cover_image: cover-picture.png
cover_image_caption: "Source: Marco Verch (https://www.flickr.com/photos/160866001@N07/50597690137/)"
toc_image: toc-picture.png
toc_image_caption: "Source: Progressive Charlestown (https://www.progressive-charlestown.com/2020/01/amazon-drivers-die-for-you.html)"
# Information for generating citation
citation:
  type: report
  doi: "10.somenumber/document.00010"
  issued: last-modified
  url: https://example.com/summarizing-output
  number: "MJ-0001"
bibliography: bibliography.bib

format: docx
---
